A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Fixed a typo in the algorithm
Avoid superscripts on subscripts, this isn't an IP paper

%At each node of the search tree, the algorithm
%labels vertices in $\V(G)$ and $\V(H)$ such that a pair $(v, w)$ with $v \in
%\V(G)$ and $w \in \V(H)$ can be added to the mapping if and only if $v$ and $w$
%have the same label.
\fi
\McSplit\ finds a maximum-cardinality mapping $M^* = \{(v_1, w_1), \dots,
(v_{|M^*|}, w_{|M^*|})\}$, where the $v_i$ are distinct members of $\V(G)$ and the
$w_i$ are distinct vertices of $\V(H)$, such that $v_i$ and $v_j$ are adjacent
in $G$ if and only if $w_i$ and $w_j$ are adjacent in $H$. 
Given such a mapping, the subgraph of $G$ induced by $\{v_i, \dots, v_{|M^*|}\}$
and the subgraph of $H$ induced by $\{w_i, \dots, w_{|M^*|}\}$ are a maximum
common subgraph.

>>>>

%At each node of the search tree, the algorithm
%labels vertices in $\V(G)$ and $\V(H)$ such that a pair $(v, w)$ with $v \in
%\V(G)$ and $w \in \V(H)$ can be added to the mapping if and only if $v$ and $w$
%have the same label.
\fi
\McSplit\ finds a maximum-cardinality mapping $M^* = \{(v_1, w_1), \dots,
(v_{m}, w_{m})\}$ with $|M^*| = m$ vertex pairs, where the $v_i$ are distinct members of $\V(G)$ and the
$w_i$ are distinct vertices of $\V(H)$, such that $v_i$ and $v_j$ are adjacent
in $G$ if and only if $w_i$ and $w_j$ are adjacent in $H$. 
Given such a mapping, the subgraph of $G$ induced by $\{v_i, \dots, v_{m}\}$
and the subgraph of $H$ induced by $\{w_i, \dots, w_{m}\}$ are a maximum
common subgraph.
